Crowdsourced geometric morphometrics enable rapid large-scale collection and

### 2015-09-17 manuscript/manuscript.Rmd
Travis: fix format_for_gpagen error
Travis: fix sequence #2

coords <- gpagen(format_for_gpagen(df, family, role, sha1mac, sequence), ShowPlot=F)$coords

@@

df <- df %>% filter(!(family == "Balistidae" & mark %in% c("D1", "D2")), !(family == "Tetraodontidae" & mark %in% c("O4", "O5")))
coords <- gpagen(format_for_gpagen(df, family, role, sha1mac, sequence), ShowPlot=F)$coords

turk_morph_pca <- pca_df(coords) %>% separate(id, c("family", "role", "ind", "seq"), sep = "_")

>>>>

coords <- gpagen(format_for_gpagen(df, family, role, sha1mac), ShowPlot=F)$coords

@@

df <- df %>% filter(!(family == "Balistidae" & mark %in% c("D1", "D2")), !(family == "Tetraodontidae" & mark %in% c("O4", "O5")))
coords <- gpagen(format_for_gpagen(df, family, role, sha1mac), ShowPlot=F)$coords

turk_morph_pca <- pca_df(coords) %>% separate(id, c("family", "role", "ind"), sep = "_")
